Methods for Large Scale Learning to Rank

### 2014-09-17 report/Chapters/Implementation.tex
impl

Setting the degree of parallelisation is crucial to obtain optimal cluster utilisation. HDInsight cluster machines offer four mapper slots and two reducer slots per data node. Cluster utilisation is optimal when the computational work is evenly distributed over exactly the number of available mappers in the map phase, and evenly distributed over exactly the number of reducers in the reduce phase. The number of mappers used can be controlled by setting MapReduce configuration parameters mapreduce.input.fileinputformat.split.maxsize, mapreduce.input.fileinputformat.split.minsize, and the Pig configuration parameter pig.maxCombinedSplitSize to the data size in bytes of the input training data divided by the number of available mappers. To control the number of used reducers, Pig offers two options: 1) the default\_parallel parameters, which can set a default number of reducers used throughout all MapReduce jobs that the Pig script consists of, and 2) the "PARALLEL" clause, which sets the number of reducers at operator level (overrides default\_parallel if set). The framework uses listed configuratoin parameters to control the numbers of mappers used and uses the "PARALLEL" clause to set the number of used reducers.

>>>>

Setting the degree of parallelisation is crucial to obtain optimal cluster utilisation. HDInsight cluster machines offer four mapper slots and two reducer slots per data node. Cluster utilisation is optimal when the computational work is evenly distributed over exactly the number of available mappers in the map phase, and evenly distributed over exactly the number of reducers in the reduce phase. The number of mappers used can be controlled by setting MapReduce configuration parameters mapreduce.input.fileinputformat.split.maxsize, mapreduce.input.fileinputformat.split.minsize, and the Pig configuration parameter pig.maxCombinedSplitSize to the data size in bytes of the input training data divided by the number of available mappers. To control the number of used reducers, Pig offers two options: 1) the default\_parallel parameters, which can set a default number of reducers used throughout all MapReduce jobs that the Pig script consists of, and 2) the "PARALLEL" clause, which sets the number of reducers at operator level (overrides default\_parallel if set). The framework uses listed configuration parameters to control the numbers of mappers used and uses the "PARALLEL" clause to set the number of used reducers. Pig code to set the number of mappers and reducers are dynamically set by the framework such that the optimal number of mappers and reducers are used.
